---
title: Codebook "Tidy Data Set of Human Activity Recognition with Smartphones"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document describes the variables of the accompanying file named 'tidy_mean_data.txt'.

##Overview

--------------------------------------
Feature                         Result
------------------------- ------------
Number of Observations             180

Number of Variables                 68

--------------------------------------

In the experiment, a participant (identified by variable 1) performed a physical activity (named by variable 2). Concurrently, acceleration data was measured by a accelerometer in gravitational acceleration (g) and angular velocity data was measured by a gyroscope in radians/second (rad/sec). These measurements were processed, normalised, summarised, and subsequently presented in variables 3-68.

```{r echo=FALSE}
x <- data.frame(c("Indicates time domain signals, originally captured at a constant rate of 50 Hz",
                  "Indicates frequency domain signals, after performing Fast Fourier Transform on the corresponding time domain signals",
                  "These 2 types of signals were obtained after filtering raw acceleration signals with a median filter and a 3rd order low pass Butterworth filter with a corner frequency of 20 Hz. Subsequently, the acceleration signal was then separated into body and gravity acceleration signals using a low pass Butterworth filter with a corner frequency of 0.3 Hz.",
                  "Indicates Jerk signals, obtained by deriving body linear acceleration or angular velocity in time",
                  "Indicates magnitude of 3-dimensional signals, calculated using Euclidean norm",
                  "Mean value of the parameter for that Subject-Activity pair",
                  "Standard deviation of the parameter for that Subject-Activity pair",
                  "Indicates direction of the signal"))
rownames(x) = c("Time",
                "Frequency",
                "BodyAcceleration, GravityAcceleration",
                "Jerk",
                "Magnitude",
                "Mean",
                "Std",
                "XYZ")
colnames(x) = "Explanation"
knitr::kable(x, caption='Legend for Understanding Variable Labels')
```



##Details and Descriptive Statistics


####Variable 1: Subject

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               integer

Number of missing obs.      0 (0 %)

Number of unique values          30

Median                         15.5

1st and 3rd quartiles         8; 23

Min. and max.                 1; 30
-----------------------------------






---

####Variable 2: Activity

--------------------------------------------------------------------------------------------------
Feature                                                                                     Result
------------------------- ------------------------------------------------------------------------
Variable type                                                                               factor

Number of missing obs.                                                                     0 (0 %)

Number of unique values                                                                          6

Levels                    LAYING, SITTING, STANDING, WALKING, WALKING UPSTAIRS, WALKING DOWNSTAIRS
                              
--------------------------------------------------------------------------------------------------






---

####Variable 3: Time\_BodyAcceleration\_Mean\_X


--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values            180

Median                            0.28

1st and 3rd quartiles       0.27; 0.28

Min. and max.                0.22; 0.3
--------------------------------------






---

####Variable 4: Time\_BodyAcceleration\_Mean\_Y


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.02

1st and 3rd quartiles       -0.02; -0.01

Min. and max.                   -0.04; 0
----------------------------------------






---

####Variable 5: Time\_BodyAcceleration\_Mean\_Z


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.11

1st and 3rd quartiles        -0.11; -0.1

Min. and max.               -0.15; -0.08
----------------------------------------






---

####Variable 6: Time\_BodyAcceleration\_Std\_X


---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                            -0.75

1st and 3rd quartiles       -0.98; -0.2

Min. and max.                  -1; 0.63
---------------------------------------






---

####Variable 7: Time\_BodyAcceleration\_Std\_Y


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.51

1st and 3rd quartiles       -0.94; -0.03

Min. and max.                -0.99; 0.62
----------------------------------------






---

####Variable 8: Time\_BodyAcceleration\_Std\_Z


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.65

1st and 3rd quartiles       -0.95; -0.23

Min. and max.                -0.99; 0.61
----------------------------------------






---

####Variable 9: Time\_GravityAcceleration\_Mean\_X


---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                             0.92

1st and 3rd quartiles        0.84; 0.94

Min. and max.               -0.68; 0.97
---------------------------------------






---

####Variable 10: Time\_GravityAcceleration\_Mean\_Y


---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                            -0.13

1st and 3rd quartiles       -0.23; 0.09

Min. and max.               -0.48; 0.96
---------------------------------------






---

####Variable 11: Time\_GravityAcceleration\_Mean\_Z


---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                             0.02

1st and 3rd quartiles       -0.12; 0.15

Min. and max.                -0.5; 0.96
---------------------------------------






---

####Variable 12: Time\_GravityAcceleration\_Std\_X


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.97

1st and 3rd quartiles       -0.98; -0.95

Min. and max.                  -1; -0.83
----------------------------------------






---

####Variable 13: Time\_GravityAcceleration\_Std\_Y


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.96

1st and 3rd quartiles       -0.97; -0.94

Min. and max.               -0.99; -0.64
----------------------------------------






---

####Variable 14: Time\_GravityAcceleration\_Std\_Z


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.95

1st and 3rd quartiles       -0.96; -0.92

Min. and max.               -0.99; -0.61
----------------------------------------






---

####Variable 15: Time\_BodyAccelerationJerk\_Mean\_X


--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values            180

Median                            0.08

1st and 3rd quartiles       0.07; 0.08

Min. and max.               0.04; 0.13
--------------------------------------






---

####Variable 16: Time\_BodyAccelerationJerk\_Mean\_Y


---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                             0.01

1st and 3rd quartiles           0; 0.01

Min. and max.               -0.04; 0.06
---------------------------------------






---

####Variable 17: Time\_BodyAccelerationJerk\_Mean\_Z


---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                                0

1st and 3rd quartiles          -0.01; 0

Min. and max.               -0.07; 0.04
---------------------------------------






---

####Variable 18: Time\_BodyAccelerationJerk\_Std\_X


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.81

1st and 3rd quartiles       -0.98; -0.22

Min. and max.                -0.99; 0.54
----------------------------------------






---

####Variable 19: Time\_BodyAccelerationJerk\_Std\_Y


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.78

1st and 3rd quartiles       -0.97; -0.15

Min. and max.                -0.99; 0.36
----------------------------------------






---

####Variable 20: Time\_BodyAccelerationJerk\_Std\_Z


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.88

1st and 3rd quartiles       -0.98; -0.51

Min. and max.                -0.99; 0.03
----------------------------------------






---

####Variable 21: Time\_BodyAngularVelocity\_Mean\_X


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.03

1st and 3rd quartiles       -0.05; -0.02

Min. and max.                -0.21; 0.19
----------------------------------------






---

####Variable 22: Time\_BodyAngularVelocity\_Mean\_Y


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.07

1st and 3rd quartiles       -0.09; -0.06

Min. and max.                 -0.2; 0.03
----------------------------------------






---

####Variable 23: Time\_BodyAngularVelocity\_Mean\_Z


---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                             0.09

1st and 3rd quartiles         0.07; 0.1

Min. and max.               -0.07; 0.18
---------------------------------------






---

####Variable 24: Time\_BodyAngularVelocity\_Std\_X


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.79

1st and 3rd quartiles       -0.97; -0.44

Min. and max.                -0.99; 0.27
----------------------------------------






---

####Variable 25: Time\_BodyAngularVelocity\_Std\_Y


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                              -0.8

1st and 3rd quartiles       -0.96; -0.42

Min. and max.                -0.99; 0.48
----------------------------------------






---

####Variable 26: Time\_BodyAngularVelocity\_Std\_Z


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                              -0.8

1st and 3rd quartiles       -0.96; -0.31

Min. and max.                -0.99; 0.56
----------------------------------------






---

####Variable 27: Time\_BodyAngularVelocityJerk\_Mean\_X


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                              -0.1

1st and 3rd quartiles        -0.1; -0.09

Min. and max.               -0.16; -0.02
----------------------------------------






---

####Variable 28: Time\_BodyAngularVelocityJerk\_Mean\_Y


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.04

1st and 3rd quartiles       -0.05; -0.04

Min. and max.               -0.08; -0.01
----------------------------------------






---

####Variable 29: Time\_BodyAngularVelocityJerk\_Mean\_Z


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.05

1st and 3rd quartiles       -0.06; -0.05

Min. and max.               -0.09; -0.01
----------------------------------------






---

####Variable 30: Time\_BodyAngularVelocityJerk\_Std\_X


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.84

1st and 3rd quartiles       -0.98; -0.46

Min. and max.                   -1; 0.18
----------------------------------------






---

####Variable 31: Time\_BodyAngularVelocityJerk\_Std\_Y


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.89

1st and 3rd quartiles       -0.98; -0.59

Min. and max.                    -1; 0.3
----------------------------------------






---

####Variable 32: Time\_BodyAngularVelocityJerk\_Std\_Z


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.86

1st and 3rd quartiles       -0.98; -0.47

Min. and max.                   -1; 0.19
----------------------------------------






---

####Variable 33: Time\_BodyAccelerationMagnitude\_Mean


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.48

1st and 3rd quartiles       -0.96; -0.09

Min. and max.                -0.99; 0.64
----------------------------------------






---

####Variable 34: Time\_BodyAccelerationMagnitude\_Std


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.61

1st and 3rd quartiles       -0.94; -0.21

Min. and max.                -0.99; 0.43
----------------------------------------






---

####Variable 35: Time\_GravityAccelerationMagnitude\_Mean


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.48

1st and 3rd quartiles       -0.96; -0.09

Min. and max.                -0.99; 0.64
----------------------------------------






---

####Variable 36: Time\_GravityAccelerationMagnitude\_Std


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.61

1st and 3rd quartiles       -0.94; -0.21

Min. and max.                -0.99; 0.43
----------------------------------------






---

####Variable 37: Time\_BodyAccelerationJerkMagnitude\_Mean


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.82

1st and 3rd quartiles       -0.98; -0.25

Min. and max.                -0.99; 0.43
----------------------------------------






---

####Variable 38: Time\_BodyAccelerationJerkMagnitude\_Std


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                              -0.8

1st and 3rd quartiles       -0.98; -0.22

Min. and max.                -0.99; 0.45
----------------------------------------






---

####Variable 39: Time\_BodyAngularVelocityMagnitude\_Mean


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.66

1st and 3rd quartiles       -0.95; -0.22

Min. and max.                -0.98; 0.42
----------------------------------------






---

####Variable 40: Time\_BodyAngularVelocityMagnitude\_Std


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.74

1st and 3rd quartiles       -0.95; -0.36

Min. and max.                 -0.98; 0.3
----------------------------------------






---

####Variable 41: Time\_BodyAngularVelocityJerkMagnitude\_Mean


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.86

1st and 3rd quartiles       -0.99; -0.51

Min. and max.                   -1; 0.09
----------------------------------------






---

####Variable 42: Time\_BodyAngularVelocityJerkMagnitude\_Std


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.88

1st and 3rd quartiles       -0.98; -0.58

Min. and max.                   -1; 0.25
----------------------------------------






---

####Variable 43: FrequencyDomain\_BodyAcceleration\_Mean\_X


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.77

1st and 3rd quartiles       -0.98; -0.22

Min. and max.                   -1; 0.54
----------------------------------------






---

####Variable 44: FrequencyDomain\_BodyAcceleration\_Mean\_Y


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.59

1st and 3rd quartiles       -0.95; -0.06

Min. and max.                -0.99; 0.52
----------------------------------------






---

####Variable 45: FrequencyDomain\_BodyAcceleration\_Mean\_Z


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.72

1st and 3rd quartiles       -0.96; -0.32

Min. and max.                -0.99; 0.28
----------------------------------------






---

####Variable 46: FrequencyDomain\_BodyAcceleration\_Std\_X


---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                            -0.75

1st and 3rd quartiles       -0.98; -0.2

Min. and max.                  -1; 0.66
---------------------------------------






---

####Variable 47: FrequencyDomain\_BodyAcceleration\_Std\_Y


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.51

1st and 3rd quartiles       -0.94; -0.08

Min. and max.                -0.99; 0.56
----------------------------------------






---

####Variable 48: FrequencyDomain\_BodyAcceleration\_Std\_Z


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.64

1st and 3rd quartiles       -0.95; -0.27

Min. and max.                -0.99; 0.69
----------------------------------------






---

####Variable 49: FrequencyDomain\_BodyAccelerationJerk\_Mean\_X


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.81

1st and 3rd quartiles       -0.98; -0.28

Min. and max.                -0.99; 0.47
----------------------------------------






---

####Variable 50: FrequencyDomain\_BodyAccelerationJerk\_Mean\_Y


---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                            -0.78

1st and 3rd quartiles       -0.97; -0.2

Min. and max.               -0.99; 0.28
---------------------------------------






---

####Variable 51: FrequencyDomain\_BodyAccelerationJerk\_Mean\_Z


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.87

1st and 3rd quartiles       -0.98; -0.47

Min. and max.                -0.99; 0.16
----------------------------------------






---

####Variable 52: FrequencyDomain\_BodyAccelerationJerk\_Std\_X


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.83

1st and 3rd quartiles       -0.98; -0.25

Min. and max.                   -1; 0.48
----------------------------------------






---

####Variable 53: FrequencyDomain\_BodyAccelerationJerk\_Std\_Y


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.79

1st and 3rd quartiles       -0.97; -0.17

Min. and max.                -0.99; 0.35
----------------------------------------






---

####Variable 54: FrequencyDomain\_BodyAccelerationJerk\_Std\_Z


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                              -0.9

1st and 3rd quartiles       -0.98; -0.54

Min. and max.               -0.99; -0.01
----------------------------------------






---

####Variable 55: FrequencyDomain\_BodyAngularVelocity\_Mean\_X


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.73

1st and 3rd quartiles       -0.97; -0.34

Min. and max.                -0.99; 0.47
----------------------------------------






---

####Variable 56: FrequencyDomain\_BodyAngularVelocity\_Mean\_Y


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.81

1st and 3rd quartiles       -0.97; -0.45

Min. and max.                -0.99; 0.33
----------------------------------------






---

####Variable 57: FrequencyDomain\_BodyAngularVelocity\_Mean\_Z


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.79

1st and 3rd quartiles       -0.96; -0.26

Min. and max.                -0.99; 0.49
----------------------------------------






---

####Variable 58: FrequencyDomain\_BodyAngularVelocity\_Std\_X


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.81

1st and 3rd quartiles       -0.98; -0.48

Min. and max.                 -0.99; 0.2
----------------------------------------






---

####Variable 59: FrequencyDomain\_BodyAngularVelocity\_Std\_Y


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                              -0.8

1st and 3rd quartiles       -0.96; -0.42

Min. and max.                -0.99; 0.65
----------------------------------------






---

####Variable 60: FrequencyDomain\_BodyAngularVelocity\_Std\_Z


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.82

1st and 3rd quartiles       -0.96; -0.39

Min. and max.                -0.99; 0.52
----------------------------------------






---

####Variable 61: FrequencyDomain\_BodyAccelerationMagnitude\_Mean


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.67

1st and 3rd quartiles       -0.96; -0.16

Min. and max.                -0.99; 0.59
----------------------------------------






---

####Variable 62: FrequencyDomain\_BodyAccelerationMagnitude\_Std


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.65

1st and 3rd quartiles       -0.95; -0.37

Min. and max.                -0.99; 0.18
----------------------------------------






---

####Variable 63: FrequencyDomain\_BodyBodyAccelerationJerkMagnitude\_Mean


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.79

1st and 3rd quartiles       -0.98; -0.19

Min. and max.                -0.99; 0.54
----------------------------------------






---

####Variable 64: FrequencyDomain\_BodyBodyAccelerationJerkMagnitude\_Std


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.81

1st and 3rd quartiles       -0.98; -0.27

Min. and max.                -0.99; 0.32
----------------------------------------






---

####Variable 65: FrequencyDomain\_BodyBodyAngularVelocityMagnitude\_Mean


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.77

1st and 3rd quartiles       -0.96; -0.41

Min. and max.                 -0.99; 0.2
----------------------------------------






---

####Variable 66: FrequencyDomain\_BodyBodyAngularVelocityMagnitude\_Std


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.77

1st and 3rd quartiles       -0.95; -0.43

Min. and max.                -0.98; 0.24
----------------------------------------






---

####Variable 67: FrequencyDomain\_BodyBodyAngularVelocityJerkMagnitude\_Mean


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.88

1st and 3rd quartiles       -0.98; -0.58

Min. and max.                   -1; 0.15
----------------------------------------






---

####Variable 68: FrequencyDomain\_BodyBodyAngularVelocityJerkMagnitude\_Std


----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.89

1st and 3rd quartiles       -0.98; -0.61

Min. and max.                   -1; 0.29
----------------------------------------
